% !TEX encoding = UTF-8 Unicode
% ÄÖÜ ß äöü

\begin{thebibliography}{10}
% \addcontentsline{toc}{section}{Quellenverzeichnis}

\bibitem{L} Aard Middeldorp. \textit{Logic (bachelor program lecture)}. Institute of Computer Science, University of Innbruck, 2011.
\url{http://cl-informatik.uibk.ac.at/teaching/ws11/lics/content.php}

\bibitem{LICS} Michael Huth and Mark Ryan. \textit{Logic in Computer Science -- Modelling and Reasoning about Systems.} Cambridge University Press, 2nd edition, 2004 (7th printing 2011). 

\bibitem{THI} Jef Raskin. \textit{The Humane Interface -- New Directions for Designing Interactive Systems.} Addison-Wesley ACM Press, 2000 (10th printing 2008). 

\bibitem{TW} Dave Barker-Plummer, Jon Barwise, John Etchemendy. \textit{Tarski's World -- Revised And Expanded.} CSLI Publications, 2008.

\bibitem{iHIG} Apple Inc.  \textit{iOS Human Interface Guidelines} March 7th, 2011. 

\url{http://developer.apple.com/library/ios/documentation/UserExperience/Conceptual/MobileHIG/}

(\href{https://developer.apple.com/library/ios/documentation/UserExperience/Conceptual/MobileHIG/MobileHIG.pdf}
{MobileHIG.pdf} 
downloaded April 21st, 2012).

% ###############
% ## 4. Entwickler ##

%\bibitem{ADOV} Apple Inc. \textit{App Development Overview} (pdf, Stand: 12.10.2011). Internet:
%\url{http://developer.apple.com/library/mac/documentation/General/Conceptual/ApplicationDevelopmentOverview/ApplicationDevelopmentOverview.pdf} (Download: 26.11.201)

%\bibitem{TEAM} Apple Inc.: \textit{About iOS Development Team Administration}
%(web, Stand: 26.11.2011). Internet: 
%\url{http://developer.apple.com/library/ios/#documentation/ToolsLanguages/Conceptual/DevPortalGuide/Introduction/Introduction.html} (Zugriff: 26.11.2011 10:10MEZ)

%\bibitem{IOSPS} Apple Inc.: \textit{Preferences and Settings Programming Guide (iOS)} (pdf, Stand: 12.10.2011). Internet: \url{http://developer.apple.com/library/ios/documentation/Cocoa/Conceptual/UserDefaults/UserDefaults.pdf} (Download: 9.11.2011 16:13MEZ)
%
%\bibitem{MACPS} Apple Inc.: \textit{Preferences and Settings Programming Guide (Mac)} (pdf, Stand: 12.10.2011). Internet: \url{http://developer.apple.com/library/mac/documentation/Cocoa/Conceptual/UserDefaults/UserDefaults.pdf} (Download: 9.11.2011 16:16MEZ)

\bibitem{iAPG} Apple Inc.  \textit{iOS App Programming Guide.} March 7th, 2012. 

\url{http://developer.apple.com/library/ios/documentation/iPhone/Conceptual/iPhoneOSProgrammingGuide/}

(\href{http://developer.apple.com/library/ios/documentation/iPhone/Conceptual/iPhoneOSProgrammingGuide/iPhoneAppProgrammingGuide.pdf} 
{iPhoneAppProgrammingGuide.pdf}
downloaded April 21st, 2012).

\bibitem{iVPG} Apple Inc.  \textit{View Programming Guide for iOS.} March 8th, 2011. 

\url{http://developer.apple.com/library/ios/documentation/WindowsViews/Conceptual/ViewPG_iPhoneOS/}

(\href{http://developer.apple.com/library/ios/documentation/WindowsViews/Conceptual/ViewPG_iPhoneOS/ViewPG_iPhoneOS.pdf}
{ViewPG\_iPhoneOS.pdf}
downloaded April 21st, 2012).

\bibitem{cCGL} Apple Inc.  \textit{Coding Guidelines for Cocoa.} February 16th, 2012. 

\url{http://developer.apple.com/library/ios/documentation/Cocoa/Conceptual/CodingGuidelines/}

(\href{http://developer.apple.com/library/ios/documentation/Cocoa/Conceptual/CodingGuidelines/CodingGuidelines.pdf}
{CodingGuidelines.pdf}
downloaded April 21st, 2012).

\bibitem{iDPG} Apple Inc.  \textit{Drawing and Printing Guide for iOS.} September 26th, 2011. 

\url{http://developer.apple.com/library/ios/documentation/2ddrawing/conceptual/drawingprintingios/}

(\href{http://developer.apple.com/library/ios/documentation/2ddrawing/conceptual/drawingprintingios/drawingprintingios.pdf}
{drawingprintingios.pdf}
downloaded April 21st, 2012).


%\bibitem{MACOSXNEW} Apple Inc.: \textit{iCloud Storage APIs} in What's new in OS X (pdf, Stand: 1 7.2011). Internet: \url{http://developer.apple.com/library/mac/releasenotes/MacOSX/WhatsNewInOSX/WhatsNewInOSX.pdf} (Download: 25.11.2011 8:00MEZ)
%
%\bibitem{IOSDB} Apple Inc.:  \textit{Document-Based Application Programming Guide for iOS} (pdf, Stand: 12.10.2011). Internet: \url{http://developer.apple.com/library/ios/documentation/DataManagement/Conceptual/DocumentBasedAppPGiOS/DocumentBasedAppPGiOS.pdf} (Download: 9.11.2011 16:09MEZ)

\end{thebibliography}

